
\begin{thebibliography}{1}
%\addcontentsline{toc}{chapter}{References}

\bibitem{kapre2016optimizing}Nachiket Kapre, \emph{Optimizing Soft Vector Processing in FPGA-based Embedded
	Systems}, \url{http://nachiket.github.io/publications/soft-vector_trets2016.pdf}

\bibitem{1}Charles Eric LaForest, \emph{High Speed Soft Processor Architecture for FPGA Overlays}, \url{http://fpgacpu.ca/octavo/High-Speed_Soft-Processor_Architecture_for_FPGA_Overlays.pdf}

\bibitem{2}Overlay Architectures for FPGA (OLAF), Berkeley. \url{http://olaf.eecs.berkeley.edu}

\bibitem{3}Michael Feldman and Addison Snell, \emph{ACCELERATED COMPUTING: A TIPPING POINT FOR HPC.}
\url{http://images.nvidia.com/content/pdf/tesla/accelerated-computing-at-a-tipping-point.pdf}

\bibitem{4}Davor Capalija and Tarek S. Abdelrahman,\emph{FPGA Overlays for High Performance Computing.} \url{https://www.eee.hku.hk/~hso/olaf2013/abdelrahman_olaf.pdf}

\bibitem{5}Kevin Morris, \emph{FPGA Wars: It’s Getting Hot at the Top.}
\url{http://www.eejournal.com/archives/articles/20130305-fpgawars}

\bibitem{6}A. K. Jain, K. D. Pham, J. Cui, S. A. Fahmy, and D. L. Maskell,\emph{Virtualized
	execution and management of hardware tasks on a hybrid ARM-FPGA platform}, 2Journal of Signal Processing Systems, 77(1–2):61–76, Oct. 2014

\bibitem{7}Jesse Benson, Ryan Cofell, Chris Frericks, Chen-Han Ho, Venkatraman Govin-
daraju, Tony Nowatzki, and Karthikeyan Sankaralingam,\emph{Design, integration
	and implementation of the dyser hardware accelerator into opensparc}, In In-
ternational Symposium on High Performance Computer Architecture (HPCA),
pages 1–12, 2012

\bibitem{8}Neil W. Bergmann, Sunil K. Shukla, and Jrgen Becker,\emph{QUKU: a dual-layer
	reconfigurable architecture}, ACM Transactions on Embedded Computing Systems
(TECS), 12:63:1–63:26, March 2013

\bibitem{9}A. Severance and G. G. F. Lemieux,\emph{Embedded supercomputing in fpgas with the
	vectorblox mxp matrix processor}, In Hardware/Software Codesign and System
Synthesis (CODES+ISSS), 2013 International Conference on, pages 1–10, 2013

\bibitem{10}Xilinx Ltd. Zynq-7000 technical reference manual\url{http://www.xilinx.com/
	support/documentation/user_guides/ug585-Zynq-7000-TRM.pdf} 2013

\bibitem{11}\url{http://www.nxp.com/assets/documents/data/en/application-notes/AN4991.pdf}

\bibitem{12}\url{http://zedboard.org/sites/default/files/documentations/ZedBoard_HW_UG_v2_2.pdf}

\bibitem{13}Xilinx Ltd. Zynq-7000 technical reference manual\url{http://www.xilinx.com/
	support/documentation/user_guides/ug585-Zynq-7000-TRM.pdf}

\bibitem{14}Gordon Brebner,\emph{A virtual hardware operating system for the Xilinx XC6200}, In
Field-Programmable Logic Smart Applications, New Paradigms and Compilers,
pages 327–336. 1996

\bibitem{15}C. Steiger, H. Walder, and M. Platzner,\emph{Operating systems for reconfigurable
	embedded platforms: online scheduling of real-time tasks}, IIEEE Transactions
on Computers, 53(11):1393–1407, November 2004

\bibitem{16}C. Aws Ismail,\emph{Operating system abstractions of hardware accelerators on field-
	programmable gate arrays}, Thesis, August 2011

\bibitem{17}Xillybus Ltd. Xillybus: IP Core Product Brief\url{http://xillybus.com/downloads/xillybus_product_brief.pdf}

\bibitem{18}\url{http://www.wiki.xilinx.com/Linux}

\bibitem{19}\url{http://vectorblox.github.io/mxp/mxp_quickstart_vivado.html}

\bibitem{20}\url{http://vectorblox.github.io/mxp/mxp_reference.html}

\bibitem{21}S. Gopalakrishnan, P. Kalla, M. B. Meredith, and F. Enescu,\emph{Finding
	linear building-blocks for RTL synthesis of polynomial datapaths with
	fixed-size bit-vectors}, ICCAD, 2007

\bibitem{22}Abhishek Kumar Jain, Douglas L. Maskell,Suhaib A. Fahmy, \emph{Throughput Oriented FPGA Overlays Using DSP Blocks.}
\url{https://www2.warwick.ac.uk/fac/sci/eng/staff/saf/publications/date2016-jain.pdf}

\bibitem{23}Soh Jun Jie and N. Kapre,\emph{Comparing soft and hard vector processing in FPGA-based embedded systems}, 2014 24th International Conference on Field Programmable Logic and Applications (FPL), Munich, 2014, pp. 1-7.
doi: 10.1109/FPL.2014.6927467

\bibitem{24}Nachiket Kapre,\emph{Optimizing Soft Vector Processing in FPGA-Based Embedded Systems}, ACM Transactions on Reconfigurable Technology and Systems, vol. 9, pp. 1, 2016, ISSN 19367406

\bibitem{25}Hormozd Benjamin Gahvari, \emph{Benchmarking Sparse Matrix-Vector Multiply.}
\url{https://pdfs.semanticscholar.org/8abd/d65f91a25d724b393f5ff07cdd3f4b033468.pdf}

\bibitem{26}Rajesh Nishtala, Richard W. Vuduc, James W. Demmel, Katherine A. Yelick, \emph{Performance Modeling and Analysis of Cache Blocking in Sparse Matrix Vector Multiply.
}
\url{https://www2.eecs.berkeley.edu/Pubs/TechRpts/2004/CSD-04-1335.pdf}



\end{thebibliography}

